Developmental trajectories of word recognition: a priming study in bilinguals

### 2023-05-05 manuscript/manuscript.qmd
Stop tracking data

# set ggplot theme and colour palette
theme_set(theme_custom()) # set custom ggplot theme
clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")

>>>>

# set ggplot theme and colour palette
theme_set(
	theme(
		panel.background = element_rect(fill = "white", colour = NA),
		panel.border = element_blank(),
		panel.grid = element_blank(),
		plot.background = element_rect(fill = "white", color = NA),
		legend.key = element_rect(fill = "white", colour = NA),
		text = element_text(colour = "black", size = 15),
		axis.text.x = element_text(size = 9),
		axis.text.y = element_text(size = 9),
		axis.line = element_line(colour = "black", size = 0.75),
		strip.text = element_text(size = 13, face = "bold"),
		strip.background = element_rect(fill = "white", colour = NA)
	)
)

# set custom ggplot theme
clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
